Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
working on summary stats

---
title: "Data Appendix to \"The impact of weather events on schooling outcomes\""
author: "Katya Garcia-Israel"
output: 
  pdf_document:
    toc: true
    number_sections: true
---

@@

export_summary_table(dfSummary(total_children))

@@

```{r regression variable specifications}
reg_data <- total_subset %>%
  mutate(lny = log(income))
```

@@

model_simple <- lm(assist ~ floods + droughts, data = reg_data)
summary(model_simple)
model_all <- lm(assist ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data)
summary(model_all)
model_register <- lm(register ~ floods + droughts + sex + age + lny + hhhead_educ + female_hhhead + urb_rur, data = reg_data)
summary(model_register)

>>>>

title: "Data Appendix to "The impact of weather events on schooling outcomes""
author: "Katya Garcia-Israel"
output:
  html_document:
    toc: yes
    df_print: paged
  pdf_document:
    toc: yes
    number_sections: yes
---

@@

export_summary_table(dfSummary(total_subset))

install.packages("stargazer")
library(stargazer)
stargazer(attitude)

@@

```{r regression variable specifications}
total_subset %>%
  mutate(ln_income = log(income))
reg_data <- total_subset %>%
  mutate(year_factor = as.factor(year))
```

@@

model_simple <- lm(assist ~ floods + droughts + year, data = reg_data)
summary(model_simple)
model_assist <- lm(assist ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + urb_rur + year, data = reg_data)
print(model_assist)
model_register <- lm(register ~ floods + droughts + age + sex + income + hhhead_educ + female_hhhead + urb_rur + year, data = reg_data)
print(model_register)

```
```{r generate regression table, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Full sample regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```
